jk test with unbalanced label

### 2016-10-19 Rmd/convergenceRatesBalancedBigK.Rmd
sync

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw()
# pE + theme_bw()
```

>>>>

```{r include=FALSE}

BEsim<- function(n){
  p<- 1
  batchN<- 1000

  dist<- abs(outer(c(yBatch), mu0, "-"))
  bayesclassified <- apply(dist, 1, function(x){c(1:K)[x==min(x)]})
  #bayes error
  (sum(bayesclassified != rep(c(1:K),each=n))/n/K/batchN)
}

bayesErorr<- BEsim(100)

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw() + geom_hline(yintercept = bayesErorr)
# pE + theme_bw()
```

### 2016-10-19 Rmd/convergenceRatesImbalanced.Rmd
sync

# if(FALSE)
{

@@

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw()
pE + theme_bw()
```

>>>>

if(FALSE)
{

@@

```{r include=FALSE}

BEsim<- function(n){
  p<- 1
  batchN<- 1000

  dist<- abs(outer(c(yBatch), mu0, "-"))

  dist<- t(t(exp(-dist^2/sigma^2/2))*c(0.25,0.75))

  bayesclassified <- apply(dist, 1, function(x){c(1:K)[x==max(x)]})
  #bayes error
  (sum(bayesclassified != c(rep(1,n/2),rep(2,n/2*3)))/n/K/batchN)
}

bayesErorr<- BEsim(100)

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw() + geom_hline(yintercept = bayesErorr)
pE + theme_bw()
```
